Meta RL analyses

### 2018-11-07 meta_RL_analyses.Rmd
Updating to analyze multiple types of runs simultaneously for the comparisons we actually want to make

```{r}
num_runs = 5
results_dir = "results/results_h256/"

@@

```{r}
load_d = function(results_dir, num_runs, file_type) {
  d = data.frame()
  for (run_i in 0:(num_runs-1)) {
    filename = sprintf("%srun%i_%s.csv", results_dir, run_i, file_type)
    if (!file.exists(filename)) {
      next
    }
    this_d = read.csv(filename, header=T) %>%
      mutate(run = run_i)
    d = bind_rows(d, this_d)
  }
  return(d)
}
```

@@

```{r}
reward_d = load_d(results_dir, num_runs, "new_rewards")

@@

```{r}
avg_reward_d = reward_d %>%
  select(-game_str) %>%
  filter(epoch == 0) %>%
  group_by(game_type, is_new_game) %>%
  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
            se_reward = sd_reward/sqrt(n()), 
            ci_lo = avg_reward - 1.96*se_reward, 
            ci_hi = avg_reward + 1.96*se_reward)
```

@@

```{r}
ggplot(avg_reward_d, aes(x=game_type, fill=is_new_game, y=avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2")
```

@@

```{r}
meta_d = load_d(results_dir, num_runs, "new_meta_true_losses")

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  gather(map_str, reward, -c(run, epoch)) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = source %in% new_game_strs | target %in% new_game_strs)
```

```{r}
avg_meta_d = meta_d %>%
  group_by(run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
            se_reward = sd_avg_reward/sqrt(n()), 
            ci_lo = avg_avg_reward - 1.96*se_reward, 
            ci_hi = avg_avg_reward + 1.96*se_reward)

@@

```{r}
ggplot(avg_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2")
```

@@

```{r}
for (emb_type in c("guess", "final")) {
  emb_d = data.frame()
  for (run_i in 0:(num_runs-1)) {
    filename = sprintf("%srun%i_%s_embeddings.csv", results_dir, run_i, emb_type)
    if (!file.exists(filename)) {
      next
    }
    this_d = read.csv(filename, header=T)
    this_d$run = run_i
    emb_d = bind_rows(emb_d, this_d)
  }

  pcs = prcomp(emb_d %>% select(-dimension, -run), center=T, scale=T)
  pc_d = data.frame(pcs$rotation)
  pc_d$task = row.names(pc_d)
  ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
    geom_point() +
    geom_text(aes(label=task)) +
    guides(color=F)
  ggsave(sprintf("plots/PCA_full_%s.png", emb_type), width=7, height=7)
}
```

>>>>

```{r}
num_runs = 20
results_dir = "results/paper_results/"

result_subdirs = c("basic", "nometa", "basic_su_heldout")

@@

```{r}
load_d = function(results_dir, result_subdirs, num_runs, file_type) {
  d = data.frame()
  for (run_i in 0:(num_runs-1)) {
    for (result_subdir in result_subdirs) {
      filename = sprintf("%s%s/run%i_%s.csv", results_dir, result_subdir, run_i, file_type)
      if (!file.exists(filename)) {
        next
      }
      this_d = read.csv(filename, header=T) %>%
        mutate(run = run_i,
               run_type=result_subdir)
      d = bind_rows(d, this_d)
      }
  }
  return(d)
}
```

@@

```{r}
reward_d = load_d(results_dir, result_subdirs, num_runs, "new_rewards")

@@

```{r}
avg_reward_d = reward_d %>%
  select(-game_str) %>%
  filter(epoch == 0) %>%
  group_by(run_type, game_type, is_new_game) %>%
  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
            se_reward = sd_reward/sqrt(n()), 
            ci_lo = avg_reward - 1.96*se_reward, 
            ci_hi = avg_reward + 1.96*se_reward)
```

@@

```{r}
ggplot(avg_reward_d, aes(x=game_type, fill=is_new_game, y=avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2") +
  facet_wrap(. ~ run_type)
```
```{r}
avg_reward_d %>% filter(is_new_game)
```

```{r}
ggplot(avg_reward_d %>% filter(is_new_game, run_type %in% c("basic", "nometa")), aes(x=run_type, fill=run_type, y=avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge", width=0.5) +
  scale_fill_brewer(palette="Set1")
```

@@

```{r}
meta_d = load_d(results_dir, c("basic", "basic_su_heldout"), num_runs, "new_meta_true_losses")

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  gather(map_str, reward, -c(run, run_type, epoch)) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = source %in% new_game_strs | target %in% new_game_strs)
```

```{r}
avg_meta_d = meta_d %>%
  group_by(run_type, run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(run_type, meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
            se_reward = sd_avg_reward/sqrt(n()), 
            ci_lo = avg_avg_reward - 1.96*se_reward, 
            ci_hi = avg_avg_reward + 1.96*se_reward)

@@

```{r}
ggplot(avg_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2") +
  facet_wrap(.~run_type)
```

@@

```{r}
for (result_subdir in result_subdirs) {
  for (emb_type in c("guess", "final")) {
    emb_d = data.frame()
    for (run_i in 0:(num_runs-1)) {
      filename = sprintf("%s%s/run%i_%s_embeddings.csv", results_dir, result_subdir, run_i, emb_type)
      if (!file.exists(filename)) {
        next
      }
      this_d = read.csv(filename, header=T)
      this_d$run = run_i
      emb_d = bind_rows(emb_d, this_d)
    }

    pcs = prcomp(emb_d %>% select(-dimension, -run), center=T, scale=T)
    pc_d = data.frame(pcs$rotation)
    pc_d$task = row.names(pc_d)
    ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
      geom_point() +
      geom_text(aes(label=task)) +
      guides(color=F)
    ggsave(sprintf("plots/%s_PCA_full_%s.png", result_subdir, emb_type), width=7, height=7)
  }
}
```
